---
title: mleary_resume
author: Matt Leary
date: "`r Sys.Date()`"
output:
  pagedown::html_resume:
    css: ['css/custom_resume.css', 'css/styles_html.css', 'resume']
    # css: ['css/custom_resume.css', 'css/styles_pdf.css', 'resume']
    # set it to true for a self-contained HTML page but it'll take longer to render
    self_contained: true
params:
  doctype: "HTML" # "PDF" or "HTML"


---


```{r setup, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)

#load packages
library(tidyverse)
library(readxl)
library(glue)

#source helper functions
source('helper_functions.R')

# turn on/off PDF versioning (will delete download link) 
# PDF <- FALSE

# get data
position_data <- readxl::read_excel('resume_data.xlsx', 
                                    sheet = "positions", 
                                    na = c("", "NA", "na")) 

skill_data <- readxl::read_excel('resume_data.xlsx', 
                                 sheet = "skills",
                                 na = c("", "NA", "na"))                                 
```


Aside
================================================================================


Contact {#contact}
--------------------------------------------------------------------------------

```{r contactinfo}

if(params$doctype == "HTML") {
  glue::glue('
    - <i class="fa fa-map-marked-alt"></i> Richmond, Virginia
    - <i class="fa fa-phone"></i> <a href="tel:+19109886368">(910) 988-6368</a>
    - <i class="fa fa-envelope"></i> mattleary311@gmail.com
    - <i class="fa fa-github"></i> [github.com/mleary](https://github.com/mleary)
    - <i class="fab fa-linkedin-in"></i> [linkedin.com/mbleary](https://www.linkedin.com/in/mbleary/)
  ')
} 

if(params$doctype == "PDF") {
  glue::glue('
    - <i class="fa fa-map-marked-alt"></i> Richmond, Virginia
    - <i class="fa fa-envelope"></i> mattleary311<!-- breaking hyplerlink -->@gmail.com
    - <i class="fa fa-github"></i> github.com/mleary
    - <i class="fab fa-linkedin-in"></i> linkedin.com/mbleary
    - <i class="fa fa-phone"></i> 910.988.6368
  ')
}

```



```{r download}

if(params$doctype == "HTML"){
  cat("[<i class='fas fa-download'></i> Download as a PDF](https://github.com/mleary/resume/raw/master/mleary_resume.pdf)")
}

```

<br>


Coding skills {#skills}
--------------------------------------------------------------------------------

```{r codingskills, dev.args = list(bg = 'transparent')}

build_skill_bars(skill_data, "Coding")

```

R skills {#rpackages}
--------------------------------------------------------------------------------

```{r rskills, dev.args = list(bg = 'transparent')}

build_skill_bars(skill_data, "R Packages")

```

Learning Focus {#interests}
--------------------------------------------------------------------------------

```{r learningfocus, dev.args = list(bg = 'transparent')}

build_skill_bars(skill_data, "Interest")

```


Disclaimer {#disclaimer}
--------------------------------------------------------------------------------



```{r}
if(params$doctype == "HTML") {
  glue::glue("
    Made w/ [**pagedown**](https://github.com/rstudio/pagedown).   
    Source code: [**Github repo**](https://github.com/mleary/resume).
  ")
} 
if(params$doctype == "PDF") {
  glue::glue("
    Made w/ **pagedown::html_resume**
    Code: **github.com/mleary/resume** 
  ")
}
```


Last updated on `r Sys.Date()`.
<br>
<br>


Main
================================================================================


Matthew Leary {#title}
--------------------------------------------------------------------------------

### Data Scientist  |  Veteran  |  Tottenham Hotspur supporter

I enjoy working with data to solve business problems and build tools that help
people work more efficiently. What I appreciate most about my job is the opportunity 
to learn new methods and techniques with each new project. Data science requires 
constant learning of technical methods, communication and presentation skills, 
and business requirements, and I find that exciting.



Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

```{r education}
print_section(position_data, 'education')
```



Professional Experience {data-icon=suitcase}
--------------------------------------------------------------------------------

```{r jobs}
print_section(position_data, 'work')
```

