---
title: mleary_resume
author: Matt Leary
date: "`r Sys.Date()`"
output:
  pagedown::html_resume:
    css: ['css/custom_resume.css', 'css/styles_html.css', 'resume']
    # css: ['css/custom_resume.css', 'css/styles_pdf.css', 'resume']
    # set it to true for a self-contained HTML page but it'll take longer to render
    self_contained: true
params:
  doctype: "HTML" # "PDF" or "HTML" is automatically updated in update_resume.R 

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)

#load packages
library(glue)

#source helper functions
source('helper_functions.R')


# get data from xlsx file
# position_data <- readxl::read_excel('resume_data.xlsx',
#                                     sheet = "positions",
#                                     na = c("", "NA", "na"))
# 
# skill_data <- readxl::read_excel('resume_data.xlsx',
#                                  sheet = "skills",
#                                  na = c("", "NA", "na"))

position_data <- read.csv('./data/position_data.csv', stringsAsFactors = F)
skill_data <- read.csv('./data/skill_data.csv', stringsAsFactors = F)
```


Aside
================================================================================


Contact {#contact}
--------------------------------------------------------------------------------

```{r contactinfo}

# Adjust contact info based on document type - html has link while pdf does not
if(params$doctype == "HTML") {
  glue::glue('
    - <i class="fa fa-map-marked-alt"></i> Richmond, Virginia
    - <i class="fa fa-phone"></i> <a href="tel:+19109886368">(910) 988-6368</a>
    - <i class="fa fa-envelope"></i> matt.leary@protonmail.com
    - <i class="fa fa-globe"></i> [mattleary.com](https://www.mattleary.com/blog/)
    - <i class="fa fa-github"></i> [github.com/mleary](https://github.com/mleary)
    - <i class="fab fa-linkedin-in"></i> [linkedin.com/mbleary](https://www.linkedin.com/in/mbleary/)
  ')
} 

if(params$doctype == "PDF") {
  glue::glue('
    - <i class="fa fa-map-marked-alt"></i> Richmond, Virginia
    - <i class="fa fa-phone"></i> 910.988.6368
    - <i class="fa fa-envelope"></i> matt.leary<!-- breaking hyplerlink -->@protonmail.com
    - <i class="fab fa-globe"></i> mattleary.com
    - <i class="fa fa-github"></i> github.com/mleary
    - <i class="fab fa-linkedin-in"></i> linkedin.com/mbleary
  ')
}

```



```{r download}
# if doctype is html add link to download a pdf version
if(params$doctype == "HTML"){
  cat("[<i class='fas fa-download'></i> Download as a PDF](https://github.com/mleary/resume/raw/main/mleary_resume.pdf)")
}

```

<br>


Tech skills {#skills}
--------------------------------------------------------------------------------

```{r codingskills, dev.args = list(bg = 'transparent')}

# function from helper_functions.R
build_skill_bars(skill_data, "Tech")

```

R skills {#rpackages}
--------------------------------------------------------------------------------

```{r rskills, dev.args = list(bg = 'transparent')}

# function from helper_functions.R
build_skill_bars(skill_data, "R Packages")

```

Learning Focus {#interests}
--------------------------------------------------------------------------------

```{r learningfocus, dev.args = list(bg = 'transparent')}

# function from helper_functions.R
build_skill_bars(skill_data, "Interests")

```


Disclaimer {#disclaimer}
--------------------------------------------------------------------------------


```{r}

# set disclaimer in bottom right corner based on doctype
if(params$doctype == "HTML") {
  glue::glue("
    Made w/ [**pagedown**](https://github.com/rstudio/pagedown).   
    Source code: [**Github repo**](https://github.com/mleary/resume).
  ")
} 
if(params$doctype == "PDF") {
  glue::glue("
    Made w/ **pagedown::html_resume**
    Code: **github.com/mleary/resume** 
  ")
}
```


Last updated on `r Sys.Date()`.
<br>
<br>


Main
================================================================================


Matthew Leary {#title}
--------------------------------------------------------------------------------

### Data Scientist  |  Veteran  |  Tottenham Hotspur supporter

I enjoy working with data to find and deliver insights, solve business problems, and build tools that help people work more efficiently. I moved into data science after 10+ years working in public policy and public relations.



Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

```{r education}
print_section(position_data, 'education')
```



Professional Experience {data-icon=suitcase}
--------------------------------------------------------------------------------

```{r jobs}
print_section(position_data, 'work')
```

